working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes

In order to test the relative effect of traits on seed production with foreign pollen we performed mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (euclidean distances). Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. Moreover, to find a model with the best explanatory traits we used the function **bioenv** from R. Finally, we also conducted mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect (develop this bit).

>>>>

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances). Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes

In order to test the relative effect of traits on seed production with
foreign pollen we performed mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (euclidean distances). Heterospecific pollen
effect was considered as the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. Moreover, to find a model with the best explanatory
traits we used the function \textbf{bioenv} from R. Finally, we also
conducted mantel test between the matrix of heterospecific pollen effect
and the distance matrix from all the traits. Moreover, We explored also
the relations between traits and heterospecific pollen effect through
generalized mixed models where the response variable was heterospecific
pollen effect (develop this bit).

>>>>

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (Euclidean distances). Heterospecific pollen
effect was considered as the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. To find a model with the best explanatory traits we
used the function \textbf{bioenv} from R. We also conducted Mantel test
between the matrix of heterospecific pollen effect and the distance
matrix from all the traits. Moreover, we explored also the correlation
between traits and heterospecific pollen effect through generalized
mixed models where the response variable was heterospecific pollen
effect and the explanatory variable the different traits.
